SAT Competition 2020\tnoteref{title}

### 2021-01-25 paper/main.tex
more conclusion

The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolio and to stimulate development of new code-bases. This rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.

Many prominent applications of SAT use an \emph{incremental} SAT solver in their backend. 
The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

>>>>

The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolios and to stimulate development of new code-bases. 
The rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base. 
Therefore, the \emph{Portfolio rule} will receive some refinement in future competitions.

Many prominent applications of SAT use an \emph{incremental} SAT solver in their backend. 
Those incremental use-cases impose additional challenges on solver authors. 
The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

The results of the \emph{Planning} track as well as our differentiated analysis of results highlight the individual contributions of many submissions. 
Our plan for future competitions is, to always run a special track for varying applications alongside the Main track.
